Synthesizing by means of mice

### 2020-08-07 mice_synthesizing/Mice_Synthesizing.Rmd
Added within and between variance over synthesizing methods

```{r, message = F}
synthetic_results <- boot_cart %>%
  map(function(x) x %$% lm(wgt ~ age + hgt)) %>%
  map_dfr(pool.syn) %T>% 
  assign("boot_syn", ., envir = globalenv()) %>%
  ci_cov(truemodel) %>%
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

@@

true_results <- bootstrap_boys %>%
  map(~ lm(wgt ~ age + hgt, .x)) %>%
  map_dfr(~ broom::tidy(.x, conf.int = TRUE)) %>%
  mutate(true_coef = rep(coef(truemodel), nsim),
         true_se   = rep(sqrt(diag(vcov(truemodel))), nsim),
         cover     = conf.low < true_coef & true_coef < conf.high) %T>% 
  assign("boot_true", ., envir = globalenv()) %>%
  group_by(term) %>%
  summarise("True Est" = unique(true_coef),
            "Boot Est"  = mean(estimate),
            "Bias"     = mean(estimate - true_coef),
            "True SE"  = unique(true_se),
            "Boot SE"   = mean(std.error),
            "DF"       = 745,
            "Lower"    = mean(conf.low),
            "Upper"    = mean(conf.high),
            "CIW"      = mean(conf.high - conf.low),
            "Coverage" = mean(cover)) %>%
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

@@

>>>>

```{r, message = F}
true_results <- bootstrap_boys %>%
  map(~ lm(wgt ~ age + hgt, .x)) %>%
  map_dfr(~ broom::tidy(.x, conf.int = TRUE)) %>%
  mutate(true_coef = rep(coef(truemodel), nsim),
         true_se   = rep(sqrt(diag(vcov(truemodel))), nsim),
         cover     = conf.low < true_coef & true_coef < conf.high) %T>% 
  assign("boot_true", ., envir = globalenv()) %>%
  group_by(term) %>%
  summarise("True Est" = unique(true_coef),
            "Boot Est"  = mean(estimate),
            "Bias"     = mean(estimate - true_coef),
            "True SE"  = unique(true_se),
            "Boot SE"   = mean(std.error),
            "DF"       = 745,
            "Lower"    = mean(conf.low),
            "Upper"    = mean(conf.high),
            "CIW"      = mean(conf.high - conf.low),
            "Coverage" = mean(cover)) %>%
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

synthetic_results <- boot_cart %>%
  map(function(x) x %$% lm(wgt ~ age + hgt)) %>%
  map_dfr(pool.syn) %T>% 
  assign("boot_syn", ., envir = globalenv()) %>%
  ci_cov(truemodel) %>%
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

@@

@@

```{r}
cart_default <- boot_cart %>%
  map(function(x) x %$% lm(wgt ~ age + hgt)) %>%
  map_dfr(pool.syn) %>%
  group_by(term) %>%
  summarise(Within = mean(ubar), Between = mean(bm), Total = mean(var))

cart_adj <- boot_cart_maxit_cp_min3 %>%
  map(function(x) x %$% lm(wgt ~ age + hgt)) %>%
  map_dfr(pool.syn) %>%
  group_by(term) %>%
  summarise(Within = mean(ubar), Between = mean(bm), Total = mean(var))

cart_default

cart_adj
```
